Safe Nuclear Power: Instrumentation, Human Oversight, and Infrastructure Transition

### 2025-06-12 Slides/PaperTwoPresentation/presentation.tex
Finished the course

% ECE4900W Communicating Engineering Solutions
% Author: Arturo Salinas-Aguayo <artjsalina5@uconn.edu>
\documentclass{beamer}
%\setbeameroption{show only notes}
\usetheme{Warsaw}
\usecolortheme{dolphin}
\usefonttheme{professionalfonts}
\setbeamertemplate{navigation symbols}{}
\usepackage{graphicx}
\usepackage{biblatex}
\addbibresource{references.bib}
\graphicspath{{../../images/}}

@@

\begin{frame}
  \begin{columns}
    \column{0.48\textwidth}
  \includegraphics[width=\textwidth]{enterprise}
    \column{0.48\textwidth}
    \begin{itemize}
      \item Nuclear power plants are designed to be safe and efficient.
      \item Instrumentation plays a critical role in monitoring and control.
      \item Human oversight is essential for safe operation.
    \end{itemize}
  \note{I've been hearing a lot of misunderstanding when it comes to this epic photograph taken on july 31, 1964 with the uss enterprise, the uss long beach, and the uss bainbridge. People generally think that the sailors aboard irrelevantly spelled $e = mc^2$. This is just a response out of ignorance however. The formula refers to the fact that as the mass of the fuel increases, the potential for it to create energy is proprotional with that multiplied times the speed of light squared. This was a demonstration of force and showing the world the US Navy's capabilities in the nuclear age. The Enterprise was the first nuclear-powered aircraft carrier with 8 submarine reactors. The uss long beach and uss bainbridge were also powered by dual surface developed reactors.}
\end{columns}
\end{frame}

@@

\begin{frame}{Human Operators: Essential Links}
  \begin{columns}
    \column{0.48\textwidth}
  \includegraphics[width=\textwidth]{maneuvering-watch.jpg}
    \note{Human operators are the last line of defense. They interpret complex data, make decisions under pressure, and ensure systems operate safely. The operators in this picutre are in a room named maneuvering. In this tight cramped space, you can see the control panel to control the reactor, and further back the electric plant control panel of a S5W reactor powered ship.}

>>>>

% ECE4900W Communicating Engineering Solutions
% Author: Arturo Salinas-Aguayo <artjsalina5@uconn.edu>
\documentclass{beamer}
%\setbeameroption{show only notes}
\usetheme{Warsaw}
\usecolortheme{dolphin}
\usefonttheme{professionalfonts}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[frame number]
\usepackage{graphicx}
\usepackage{biblatex}
\addbibresource{references.bib}
\graphicspath{{../../images/}}

@@

\begin{frame}
  \begin{columns}
    \column{0.48\textwidth}
  \includegraphics[width=\textwidth]{enterprise}
    \column{0.48\textwidth}
    \begin{itemize}
      \item Nuclear power plants are designed to be safe and efficient.
      \item Instrumentation plays a critical role in monitoring and control.
      \item Human oversight is essential for safe operation.
    \end{itemize}
  \note{I've been hearing a lot of misunderstanding when it comes to this photograph taken on july 31, 1964 with the uss enterprise, the uss long beach, and the uss bainbridge. I've heard  generally think that the sailors aboard irrelevantly spelled $e = mc^2$. This is just a response out of ignorance however. The formula refers to the fact that as the mass of the fuel increases, the potential for it to create energy is proprotional with that multiplied times the speed of light squared. This was a demonstration of force and showing the world the US Navy's capabilities in the nuclear age. The Enterprise was the first nuclear-powered aircraft carrier with 8 submarine reactors. The uss long beach and uss bainbridge were also powered by dual surface developed reactors.}
\end{columns}
\end{frame}

@@

\subsection{Technological Impact}
\begin{frame}{Human Operators: Essential Links}
  \begin{columns}
    \column{0.48\textwidth}
  \includegraphics[width=\textwidth]{maneuvering-watch.jpg}
    \note{Human operators are the last line of defense. They interpret complex data, make decisions under pressure, and ensure systems operate safely. The operators in this picutre are in a room named maneuvering. In this tight cramped space, you can see the control panel to control the reactor, and further back the electric plant control panel of a S5W reactor powered ship.}
